\documentclass[11pt,a4paper]{article}
%\usepackage{mathtools,comicsans}
%\usepackage{babel}
\usepackage[utf8]{inputenc}
\usepackage[left=2.5cm,right=2cm, bottom=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{import}
%\usepackage{subfig}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color}
\usepackage{abstract}
\usepackage{braket}
\usepackage{float}
\usepackage[toc,page]{appendix}
%\usepackage{url}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{titling}

\usepackage{tabularx}
%\usepackage{subfigure}
\usepackage{listings}
\DeclareUnicodeCharacter{2212}{-}
\graphicspath{ {./res/} } % Sets path to folder with images/figures

\setlength {\marginparwidth }{2cm}
\usepackage{todonotes}

\usepackage{biblatex}
\addbibresource{bibliography.bib}


%\renewcaptionname\figureautorefname{Fig.}
\renewcommand{\figureautorefname}{Fig.}
\renewcommand{\figurename}{Fig.}

\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}

%% Algorithm
\usepackage{listings}
\lstset{language=C++}
\lstset{
        mathescape=true,
        morekeywords={if,then,else,return}
        }
\lstset{ 
    captionpos=t,
    tabsize=2
}
\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}
\renewcommand{\lstlistingname}{Algorithm}% Listing -> Algorithm
\renewcommand{\lstlistlistingname}{List of \lstlistingname s}% List of Listings -> List of Algorithms

\lstset{
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{green}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red} % string color
    basicstyle=\footnotesize\ttfamily
}

\author{Mario R. Hiti}
\date{\today}
\title{Selected Topics for Computational Electronics}


% double underline
\def\doubleunderline#1{\underline{\underline{#1}}}

\begin{document}
%%%%%%%%% TITLE PAGE %%%%%%%%%
\maketitle



%\listoftodos
\begin{abstract}
    OpenVDB and NanoVDB are data structures which were initially developed for image and movie rendering.
    However it is possible to use the provided frameworks within the context of semiconductor process simulation.
    This paper aims to benchmark the raytracing performance of NanoVDB and OpenVDB for said application in a worst-case scenario on a small scientific computing cluster.
    NanoVDB, which is a mini-version of OpenVDB, is also compatible with common graphics APIs.
    Therefore it's behavior on GPUs and it's accuracy is examined as well.
    The benchmarks shows that NanoVDB performs at least 6x faster on a GPU compared to OpenVDB on similarly priced hardware.
    However the accuracy of NanoVDB is limited by the grid's voxel size.
\end{abstract}


\tableofcontents



\newpage
\setcounter{page}{1}


%%%%%%%%% Begin Document %%%%%%%%%
\input{1-introduction}
\input{2-methology}
\include{3-results}
\input{4-discussion}
\input{5-conclusions}
\include{6-appendix}

\printbibliography

\end{document}